paper

### 2024-09-12 paper.qmd
.

# Run LimROTS analysis with trend and robust settings enabled
rots.result <- LimROTS(data.exp = UPS1.Case0, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)
```

>>>>

# Set metadata and formula for LimROTS analysis
meta.info <- "Conc."
B <- 1000  # Number of bootstrap samples
K <- dim(UPS1.Case0)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 10  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "Conc."
formula.str <- "Conc."

# Run LimROTS analysis with trend and robust settings enabled
rots.result <- LimROTS(data.exp = UPS1.Case0, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, n.ROTS = TRUE)
```

## Run limma

library(limma)

data("UPS1.Case0")

data <- assay(UPS1.Case0)

formula.str <- "~ 0 + Conc."

meta.info <- data.frame(colData(UPS1.Case0), check.names = FALSE, row.names = row.names(colData(UPS1.Case0)))

meta.info$sample.id <- NULL

design.matrix <- model.matrix(formula(formula.str), data = meta.info)

colnames(design.matrix) <- make.names(colnames(design.matrix))

fit <- lmFit(data, design.matrix)

cont_matrix <- makeContrasts("Conc.1-Conc.2",  levels=design.matrix)

fit2 <- contrasts.fit(fit, cont_matrix)

fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)

limma.result <- topTable(fit.ebayes, coef="Conc.1-Conc.2" , number = "Inf")

```
